Leadership across cultures and contexts: an exploratory analysis

### 2020-04-16 leadership_across_cultures_contexts.Rmd
Many edits

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=F)
source('analyses2.R')
library(pander)
```

@@

@@

```{r doc-years, fig.height=6, fig.cap="Historgram of eHRAF document publiction year. Vertical line shows the mean publication year."}
doc_year_hist
```

@@

```{r field-years, fig.height=8, fig.width=9, fig.cap="Dumbbell plot of eHRAF document field work years. Vertical lines shows the  mean earliest and latest years of field work."}
doc_fielddates_plot
```

@@

Figure \@ref(fig:highstatusplot) depicts the `r length(highstatus_plot$data$Word)` words with non-zero (mostly positive) coefficents. The words most predictive of evidence for high status leaders are *`r rev(highstatus_plot$data$Word)[1:3]`*, and *`r rev(highstatus_plot$data$Word)[4]`*, respectively. The words, *`r rev(highstatus_plot$data$Word)[5:7]`* are moderately strong predictors.

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=F)
source('analyses2.R')
library(pander)
library(patchwork)
```

@@

We then explored relationships between total leader benefits and costs, summed across all leader benefit and cost variables, respectively, and levels of social and political organization. In general, leaders at the highest supracommunity level had the most evidence for receiving benefits and the least evidence for suffering costs. See Figure \@ref(fig:leadertotalbenefitscosts).

```{r leadertotalbenefitscosts, fig.cap="Estimated marginal means of A. leader total benefits, and B. total costs, as a function of group structure, based on a Poisson mixed effects regression model with random intercepts for ethnographer nested within culture. Values are on the response scale."}
p1 <- 
  emm_plot(emmeans(m_ldrtotben, type = 'response', specs = 'group.structure2')) +
  labs(title = "Total leader benefits", x = "", y = "")

p2 <- emm_plot(emmeans(m_ldrtotcost, type = 'response', specs = 'group.structure2')) +
  labs(title = "Total leader costs", x = "\nRate", y = "")

p1 + p2 + plot_layout(ncol = 1) + plot_annotation(tag_levels = 'A')

@@

```{r doc-years, fig.height=6, fig.cap="Historgram of eHRAF document publiction year. Vertical line shows the median publication year."}
doc_year_hist
```

@@

```{r field-years, fig.height=8, fig.width=9, fig.cap="Span of fieldwork years of study documents. To improve clarity, one document with very early fieldwork from 1791-1804 was omitted."}
doc_fielddates_plot
```

@@

Figure \@ref(fig:highstatusplot) depicts the `r length(highstatus_plot$data$Word)` words with non-zero (mostly positive) coefficents. The words most predictive of evidence for high status leaders are *`r rev(highstatus_plot$data$Word)[1:4]`*, and *`r rev(highstatus_plot$data$Word)[5]`*.

We then investigated if the proportion of text records with evidence for high status differed among the different levels of social and political organization. There were modest differences. Somewhat counterintuitively, the proportion of text records indicating high status was lowest at the highest level of political organization, perhaps because it would have been superfluous to note that kings and chiefs were high status. See Figure \@ref(fig:groupstatus).

```{r groupstatus, fig.cap="Estimated marginal means of a mixed effects logistic regression model of evidence for high status (0/1) as a function of group type, with random effects for ethnographer nested within culture."}
plot_emm_status_group
```
